Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-28 thesis.Rmd
lite ändringar i metod och lagt till en mer korrekt version av första meningen för diskussion.

## Main results
The adjusted analyses showed only statistical significance when comparing BE class 4 to class 1, which had 63% lower odds for OFI (OR 0,37; 95% CI 0,14-0,83; p-value 0.026).

The un-adjusted analysis showed when comparing to class 1 in BE group, class 2 (OR 1,61; 95% CI 1,17-2,20; p-value 0.003) and 3 (OR 1,91; 95% CI 1,08-3,16; p-value 0.018) were significant in increased risk for OFI. For the SBP group, comparison between class 1 and class 4 showed significant increased risk (OR 2,28; 95% CI 1,26-3,85; p-value 0.004).

@@

-->
```
This study aims to describe the types of opportunities for improvement for adult trauma patients arriving in shock, and to assess how the degree of shock is associated with opportunities for improvement.

>>>>

## Main results
The adjusted analyses showed only statistical significance when comparing BE class 4 to class 1, which had 63% reduced odds for OFI (OR 0,37; 95% CI 0,14-0,83; p-value 0.026).

The un-adjusted analysis showed when comparing to class 1 in BE group, class 2 and 3 increased odds for OFI by 61% (OR 1,61; 95% CI 1,17-2,20; p-value 0.003) respective 91% (OR 1,91; 95% CI 1,08-3,16; p-value 0.018). The SBP group showed, when comparing class 4 to class 1, there were increased odds of 128% (OR 2,28; 95% CI 1,26-3,85; p-value 0.004).

@@

-->
```
## Key results
We found that the most common type of OFI is Clinical judgement error across almost all shock severities and that there are minor if any association between shock severity and OFI.

## Limitations

## Clinical applications

## Future studies
This study aims to describe the types of opportunities for improvement for adult trauma patients arriving in shock, and to assess how the degree of shock is associated with opportunities for improvement.
